CFTP Convergence

### 2024-12-18 extensive_tests/CFTP_convergence/draft-test_CFTP_convergence.Rmd
Updating config CFTP convergence test to run simulations in australia
Adding script for rule to get CpG counts at island and non island structures for a reference genome and updating draft abc inferences vignette
Updating snakemake workflow for test CFTP convergence until run_sim

- R packages:

@@

- An .RData file with a dataframe specifying the distribution of methylation sites in the genomic region.

@@

- `run_sim.R`. TODO: Update way in which the package is loaded before submitting.

>>>>

- Dependencies are on: `environment.yaml`

@@

- An .RData file with a dataframe specifying the distribution of methylation sites in the genomic region (under the same Snakemake directory)

-

@@

- `run_sim.R`. TODO: Update way in which the package is loaded before submitting. Uses as many cores as the config param n_sim

## Running the workflow with nohup

When using nohup one needs to activate the environment in the command.

```{bash, eval = FALSE}
# E.g. running the run_sim rule
nohup conda run -n cftp_testConvergence snakemake run_sim &
```
